---
title: "Individual CS"
author: "Austin Jia"
date: "11/28/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Libraries

```{r, echo = FALSE, include = FALSE}
# Installing packages
pkgTest <- function(x) {
  if (!require(x,character.only = TRUE)) {
    install.packages(x,dep=TRUE)
  }
}
pkgs <- c("jsonlite", "dplyr", "rvest", "purrr", "ggplot2", "gganimate", "ggthemes", "lubridate", "zoo", "shiny", "stringr", "mice", "VIM", "parallel", "corrplot", "MASS")
for (pkg in pkgs) {
  pkgTest(pkg)
}
```

```{r, include=FALSE, echo = FALSE}
library(jsonlite)
library(dplyr)
library(rvest)
library(purrr)
library(ggplot2)
library(gganimate)
library(ggthemes)
library(lubridate)
library(zoo)
library(shiny)
library(stringr)
library(mice)
library(VIM)
library(parallel)
library(corrplot)
library(MASS)
library(caTools)
```

### Scraping
### Page by page method

```{r}
base_url = "https://data.cityofnewyork.us/Education/2016-2017-School-Quality-Report-Elem-Middle-K-8-Sc/9n2i-9h9s/data"
p = read_html(base_url)

school_quality = tibble(
  "Student Achievement Rating" = p %>%
    html_nodes("td:nth-child(11) div") %>%
    html_text()
) 
school_quality
```




### Yellow Pages Method

```{r}
count = 0

for(numPage in 1:2){

        # Create and read the page address
        page = paste('https://data.cityofnewyork.us/Education/2016-2017-School-Quality-Report-Elem-Middle-K-8-Sc/9n2i-9h9s/data/?page', '=', numPage)
        nPage <- str_replace_all(page, pattern=" ", repl="")

        # Read the 20 items of each the page
        for(numItem in 1:3){

                print(paste(' -- Reading the item', numItem, ' on page', numPage))

                item =  paste('item', numItem, sep = "", collapse = NULL)
                xPath <- paste("//*[@id=',item, ']", sep = "'", collapse = NULL)

                # read the path
                readPath <- nPage %>% read_html() %>% html_nodes(xpath = xPath)

                # Get values
                student_achievement_rating  <- readPath %>% html_nodes(".table-responsive:nth-child(7) td:nth-child(11) div") %>% html_text(trim = TRUE)
                
                print(student_achievement_rating)
                
                lengthStudentachievementrating <- length(student_achievement_rating)
                
                print(lengthStudentachievementrating)

                enrollment <- readPath %>% html_nodes("td:nth-child(4) div") %>% html_text(trim = TRUE)
                lengthEnrollment <- length(enrollment)

                school_type <- readPath %>% html_nodes("td:nth-child(3) div") %>% html_text(trim = TRUE)
                lengthSchooltype <- length(school_type)

                if(lengthStudentachievementrating == 0){

                        student_achievement_rating = 'NA'

                }

                if(lengthEnrollment == 0){

                        enrollment = 'NA'

                }

                if(lengthSchooltype == 0){

                        school_type = 'NA'

                }

                # Store variables
                if(count == 0){

                        vectorStudentachievementrating <- student_achievement_rating
                        vectorEnrollment <- enrollment
                        vectorSchooltype <- school_type
                }else{

                        vectorStudentachievementrating <- c(vectorStudentachievementrating, student_achievement_rating)
                        vectorEnrollment <- c(vectorEnrollment, enrollment)
                        vectorSchooltype <- c(vectorSchooltype, school_type)

                }


                count = count + 1

        }


}


df <- data.frame(vectorStudentachievementrating, vectorEnrollment, vectorSchooltype)

df
```

### Data 

```{r}
data <- read.csv("schooldata.csv")

#Renaming variable names
data = data %>% 
  rename(
    Instruction.Rating = Rigorous.Instruction.Rating,
    Teachers.Rating = Collaborative.Teachers.Rating,
    Leadership.Rating = Effective.School.Leadership.Rating,
    Community.Ties.Rating = Strong.Family.Community.Ties.Rating,
    Instruction.Rating.pct = Rigorous.Instruction...Percent.Positive,
    Teachers.Rating.pct = Collaborative.Teachers...Percent.Positive,
    Supportive.Environment.pct = Supportive.Environment...Percent.Positive,
    Leadership.Rating.pct = Effective.School.Leadership...Percent.Positive,
    Community.Ties.Rating.pct = Strong.Family.Community.Ties...Percent.Positive,
    Challenging.Curriculum.qr = Quality.Review...How.interesting.and.challenging.is.the.curriculum.,
    Effective.Teaching.qr = Quality.Review...How.effective.is.the.teaching.and.learning.,
    School.Assess.qr = Quality.Review...How.well.does.the.school.assess.what.students.are.learning.,
    Expectations.Communicated.qr = Quality.Review...How.clearly.are.high.expectations.communicated.to.students.and.staff.,
    Teachers.Cooperation.qr = Quality.Review...How.well.do.teachers.work.with.each.other.,
    Safe.Inclusive.qr = Quality.Review...How.safe.and.inclusive.is.the.school.while.supporting.social.emotional.growth.,
    Resource.Allocation.qr = Quality.Review...How.well.does.the.school.allocate.and.manage.resources.,
    Meet.Goals.qr = Quality.Review...How.well.does.the.school.identify..track..and.meet.its.goals.,
    Teacher.Development.qr = Quality.Review...How.thoughtful.is.the.school.s.approach.to.teacher.development.and.evaluation.,
    Decisions.Evaluated.qr = Quality.Review...How.well.are.school.decisions.evaluated.and.adjusted.,
    Review.Dates.qr = Quality.Review...Dates.of.Review,
    ELA.Proficiency = Average.Incoming.ELA.Proficiency..Based.on.4th.Grade.,
    Math.Proficiency = Average.Incoming.Math.Proficiency..Based.on.4th.Grade.,
    Principal.Experience.yrs = Years.of.principal.experience.at.this.school, 
    Teachers.3yrs.Experience = Percent.of.teachers.with.3.or.more.years.of.experience,
    Students.Chronically.Absent = Percent.of.Students.Chronically.Absent
    )

#Replacing blank levels with NAs
data <- data %>% mutate_if(is.factor, list(~factor(replace(., .=="", NA))))

#Removing Collinear/Redundant Data
data_numeric = data[ , purrr::map_lgl(data, is.numeric)]
corrplot(cor(data_numeric, use="pairwise.complete.obs"), method = "circle", tl.cex=0.5)

redundant_cols = c("Instruction.Rating", "Supportive.Environment.Rating", "Community.Ties.Rating", "Teachers.Rating", "Leadership.Rating", "Trust.Rating")
data = data[ , -which(names(data) %in% redundant_cols)]
colnames(data)
```
I removed all the columns that included subjective ratings for collinearity reasons. For example, Supportive.Environment.Rating, which categorizes the supportiveness of a school's environment, would be highly collinear with Supportive.Environment.Rating.pct, which captures the percent of the school population that believes that the school's environment is supportive. 


### Missing Data

```{r}
sum(is.na(data)) / (dim(data)[1] * dim(data)[2])
nrow(data[complete.cases(data), ])
nrow(data[complete.cases(data), ])/nrow(data)
```

```{r}
missing.prop <- apply(data, MARGIN = 2, FUN = function(x) { sum(is.na(x)) })
missing.prop <- missing.prop / dim(data)[1]
missing.prop <- data.frame("prop" = missing.prop,
                           "var" = names(data))
ggplot(missing.prop, aes(x = reorder(var, -prop), y = prop)) + 
  geom_bar(stat = "identity") +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + 
  geom_col(colour = "black", fill = "#FF6666") + 
  xlab("Covariate") + 
  ylab("Proportion Missing") +
  ggtitle("The Proportion of Missing Values for Each Covariate")
```

Some initial data exploration tells us that our data is missing about 16% of its values. That 16% missing data is distributed in such a way that only 10% of our observations (123 schools) have complete information. The plot showcases some of the most problematic covariates in terms of missing data. 

We suspected that the Economic Need Index might have some effect on the presence of several key variables in the dataset. Firstly, we observed that there are no data points missing with the Year of Cardiac Catherization variable.Because we have no missing values of the Economic Need Index variable, margin plots will not make sense here because there will not exist a subset of the data for which the variable is missing. We will look at the distribution of present/missing data across time for the top 2 covariates with the largest missing proportion. 

```{r}
#Not MCAR

marginplot(data[, c("Teacher.Attendance.Rate", "ELA.Proficiency")], col = mdc(1:2), cex.numbers = 1.2, pch = 19)

marginplot(data[, c("Teacher.Attendance.Rate", "Math.Proficiency")], col = mdc(1:2), cex.numbers = 1.2, pch = 19)
```

Looking at the distributions, we can see that the missngness of Math and ELA proficiency seems very different depending on the teacher attendance, indicating that the covariates are not MCAR. This could be because when teachers are absent during data collection days, ELA and Math proficiency of their class' students is not recorded. 

To avoid complete case analysis and other ways of dealing with missing data that would systematically change the distribution of our outcome patterns and thus bias our analysis results, we turn to Multiple Imputation methods to instead generate conditional distributions on the missingness of our data. 

We used mean/mode imputation to impute the covariates that were missing values within the threshold of 0% to 5%. This is because the results of doing mean imputation in covariates with only a small amount of missing values will not differ significantly from doing MICE on all covariates, which would have taken a lot more time. In the graph below, we can see that after doing mean imputation on the covariates missing small amounts of data, only the covariates missing significant amounts of data are left. We will use MICE to perform imputation with these covariates.

```{r, include=FALSE}
#Mean imputation 
impute_covariates <- as.character(missing.prop[(missing.prop$prop <= 0.1) & (missing.prop$prop > 0), ]$var)
data2 <- as.data.frame(data)
for (var in impute_covariates) {
    data2[is.na(data2[[var]]), var] <- mean(data2[[var]], na.rm = TRUE)
}

colnames(data)[colSums(is.na(data)) > 0]
colnames(data2)[colSums(is.na(data2)) > 0]
```

We used MICE, or Multiple Imputation using Chained Equations, to created our imputed datasets. We created 4 imputed datasets, roughly corresponding to the percent of missing data. 

```{r, include=FALSE}
if (!file.exists("mice.rds")) {
  start_time <- Sys.time()
  data3 <- parlmice(data2, m=4, printFlag=FALSE, maxit = 5,
                  cluster.seed=123, n.core = 2, n.imp.core = 4, cl.type = "FORK")
  end_time <- Sys.time()
  end_time - start_time
} else {
  data3 <- readRDS("mice.rds")
}
```

### EDA - General

```{r}
#Response Variable
data2$Student.Achievement.Rating <- factor(data2$Student.Achievement.Rating,levels = c("Not Meeting Target", "Approaching Target", "Meeting Target", "Exceeding Target", "NA"))

g1 = ggplot(data2, aes(factor(Student.Achievement.Rating),fill = Student.Achievement.Rating)) +
geom_bar(stat="count", position = "dodge") + 
scale_fill_brewer(palette = "Set1") + ggtitle("Student Achievement Rating Distribution") + xlab("Student Achievement Rating") + labs(fill = "Target Category") + theme(axis.text.x=element_text(angle=45, hjust=1))

g1

#Racial Breakdown
g2 = ggplot(data2,aes(x=Percent.Asian,fill=factor(Student.Achievement.Rating)))+geom_density(alpha=0.25)+
  geom_vline(aes(xintercept=mean(Percent.Asian[Student.Achievement.Rating=="Not Meeting Target"],na.rm=T)),color="red",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Asian[Student.Achievement.Rating=="Approaching Target"],na.rm=T)),color="blue",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Asian[Student.Achievement.Rating=="Meeting Target"],na.rm=T)),color="green",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Asian[Student.Achievement.Rating=="Exceeding Target"],na.rm=T)),color="purple",linetype="dashed",lwd=1)+
  scale_x_continuous(breaks = seq(8,15,1))+
  xlab(label = "Percent Asian")+
  ggtitle("Distribution of Percentage Asian")+
  theme_classic() + labs(fill = "Student Achievement Rating")

g2

g3 = ggplot(data2,aes(x=Percent.Hispanic,fill=factor(Student.Achievement.Rating)))+geom_density(alpha=0.25)+
  geom_vline(aes(xintercept=mean(Percent.Hispanic[Student.Achievement.Rating=="Not Meeting Target"],na.rm=T)),color="red",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Hispanic[Student.Achievement.Rating=="Approaching Target"],na.rm=T)),color="blue",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Hispanic[Student.Achievement.Rating=="Meeting Target"],na.rm=T)),color="green",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Hispanic[Student.Achievement.Rating=="Exceeding Target"],na.rm=T)),color="purple",linetype="dashed",lwd=1)+
  scale_x_continuous(breaks = seq(8,15,1))+
  xlab(label = "Percent Hispanic")+
  ggtitle("Distribution of Percentage Hispanic")+
  theme_classic()+ labs(fill = "Student Achievement Rating")

g4 = ggplot(data2,aes(x=Percent.Asian,fill=factor(Student.Achievement.Rating)))+geom_density(alpha=0.25)+
  geom_vline(aes(xintercept=mean(Percent.Asian[Student.Achievement.Rating=="Not Meeting Target"],na.rm=T)),color="red",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Asian[Student.Achievement.Rating=="Approaching Target"],na.rm=T)),color="blue",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Asian[Student.Achievement.Rating=="Meeting Target"],na.rm=T)),color="green",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Asian[Student.Achievement.Rating=="Exceeding Target"],na.rm=T)),color="purple",linetype="dashed",lwd=1)+
  scale_x_continuous(breaks = seq(8,15,1))+
  xlab(label = "Percent Asian")+
  ggtitle("Distribution of Percentage Asian")+
  theme_classic()+ labs(fill = "Student Achievement Rating")

g5 = ggplot(data2,aes(x=Percent.Black,fill=factor(Student.Achievement.Rating)))+geom_density(alpha=0.25)+
  geom_vline(aes(xintercept=mean(Percent.Black[Student.Achievement.Rating=="Not Meeting Target"],na.rm=T)),color="red",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Black[Student.Achievement.Rating=="Approaching Target"],na.rm=T)),color="blue",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Black[Student.Achievement.Rating=="Meeting Target"],na.rm=T)),color="green",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.Black[Student.Achievement.Rating=="Exceeding Target"],na.rm=T)),color="purple",linetype="dashed",lwd=1)+
  scale_x_continuous(breaks = seq(8,15,1))+
  xlab(label = "Percent Black")+
  ggtitle("Distribution of Percentage Black")+
  theme_classic()+ labs(fill = "Student Achievement Rating")

g6 = ggplot(data2,aes(x=Percent.White,fill=factor(Student.Achievement.Rating)))+geom_density(alpha=0.25)+
  geom_vline(aes(xintercept=mean(Percent.White[Student.Achievement.Rating=="Not Meeting Target"],na.rm=T)),color="red",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.White[Student.Achievement.Rating=="Approaching Target"],na.rm=T)),color="blue",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.White[Student.Achievement.Rating=="Meeting Target"],na.rm=T)),color="green",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.White[Student.Achievement.Rating=="Exceeding Target"],na.rm=T)),color="purple",linetype="dashed",lwd=1)+
  scale_x_continuous(breaks = seq(8,15,1))+
  xlab(label = "Percent Asian")+
  ggtitle("Distribution of Percentage Asian")+
  theme_classic()+ labs(fill = "Student Achievement Rating")

#Faculty Experience
g7 = ggplot(data2,aes(x=Principal.Experience.yrs,fill=factor(Student.Achievement.Rating)))+geom_density(alpha=0.25)+
  geom_vline(aes(xintercept=mean(Principal.Experience.yrs[Student.Achievement.Rating=="Not Meeting Target"],na.rm=T)),color="red",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Principal.Experience.yrs[Student.Achievement.Rating=="Approaching Target"],na.rm=T)),color="blue",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Principal.Experience.yrs[Student.Achievement.Rating=="Meeting Target"],na.rm=T)),color="green",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Principal.Experience.yrs[Student.Achievement.Rating=="Exceeding Target"],na.rm=T)),color="purple",linetype="dashed",lwd=1)+
  scale_x_continuous(breaks = seq(8,15,1))+
  xlab(label = "Principal Experience (yrs)")+
  ggtitle("Distribution of Principal Experience")+
  theme_classic()+ labs(fill = "Student Achievement Rating")

g8 = ggplot(data2,aes(x=Teachers.3yrs.Experience,fill=factor(Student.Achievement.Rating)))+geom_density(alpha=0.25)+
  geom_vline(aes(xintercept=mean(Teachers.3yrs.Experience[Student.Achievement.Rating=="Not Meeting Target"],na.rm=T)),color="red",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Teachers.3yrs.Experience[Student.Achievement.Rating=="Approaching Target"],na.rm=T)),color="blue",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Teachers.3yrs.Experience[Student.Achievement.Rating=="Meeting Target"],na.rm=T)),color="green",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Teachers.3yrs.Experience[Student.Achievement.Rating=="Exceeding Target"],na.rm=T)),color="purple",linetype="dashed",lwd=1)+
  scale_x_continuous(breaks = seq(8,15,1))+
  xlab(label = "Teacher Experience (% More than 3 yrs)")+
  ggtitle("Distribution of Teacher Experience")+
  theme_classic()+ labs(fill = "Student Achievement Rating")

#Financial Circumstances
g10 = ggplot(data2,aes(x=Economic.Need.Index,fill=factor(Student.Achievement.Rating)))+geom_density(alpha=0.25)+
  geom_vline(aes(xintercept=mean(Economic.Need.Index[Student.Achievement.Rating=="Not Meeting Target"],na.rm=T)),color="red",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Economic.Need.Index[Student.Achievement.Rating=="Approaching Target"],na.rm=T)),color="blue",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Economic.Need.Index[Student.Achievement.Rating=="Meeting Target"],na.rm=T)),color="green",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Economic.Need.Index[Student.Achievement.Rating=="Exceeding Target"],na.rm=T)),color="purple",linetype="dashed",lwd=1)+
  scale_x_continuous(breaks = seq(8,15,1))+
  xlab(label = "Economic Need Index")+
  ggtitle("Distribution of Economic Need Index")+
  theme_classic()+ labs(fill = "Student Achievement Rating")

g11 = ggplot(data2,aes(x=Percent.in.Temp.Housing,fill=factor(Student.Achievement.Rating)))+geom_density(alpha=0.25)+
  geom_vline(aes(xintercept=mean(Percent.in.Temp.Housing[Student.Achievement.Rating=="Not Meeting Target"],na.rm=T)),color="red",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.in.Temp.Housing[Student.Achievement.Rating=="Approaching Target"],na.rm=T)),color="blue",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.in.Temp.Housing[Student.Achievement.Rating=="Meeting Target"],na.rm=T)),color="green",linetype="dashed",lwd=1)+
  geom_vline(aes(xintercept=mean(Percent.in.Temp.Housing[Student.Achievement.Rating=="Exceeding Target"],na.rm=T)),color="purple",linetype="dashed",lwd=1)+
  scale_x_continuous(breaks = seq(8,15,1))+
  xlab(label = "% Students in Temporary Housing")+
  ggtitle("Distribution of Students in Temporary Housing")+
  theme_classic()+ labs(fill = "Student Achievement Rating")
```


### Modeling

Logistic  - for interpretation
Random Forest - for predictive power

```{r}

```


### Model Selection

```{r}
set.seed(123)   #  set seed to ensure you always have same random numbers generated
rows <- sample(nrow(data2))
data2 <- data2[rows, ]
sample = sample.split(data2,SplitRatio = 0.75) # splits the data in the ratio mentioned in SplitRatio. After splitting marks these rows as logical TRUE and the the remaining are marked as logical FALSE
train =subset(data2,sample ==TRUE) # creates a training dataset named train1 with rows which are marked as TRUE
test=subset(data2, sample==FALSE)
train = na.omit(train)
test = na.omit(test)
```

### Visualizaitons (R Shiny)

### Conclusions

### To Do
- Data Scraping
- Excluding Collinear covariates
- Excluding QR covariates
- Modeling
- CV
- Visualizations

Questions
- Binary Logistic vs. Multinomial Logistic?
- How to scrape data?
- MICE not working?